Parameter Inference\\with Bifurcation Diagrams

### 2021-06-11 docs/checklist.tex
submitting to neurips
rename package

\item If you ran experiments...
\begin{enumerate}
  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
    \answerYes{Figures can be reproduced using unit tests in the GitHub repository for \texttt{BifurcationFit.jl}}
  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
    \answerYes{In Section \ref{section:results} we details of optimisations with \texttt{Flux.jl}}
	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
    \answerYes{In Section \ref{section:results} we include error bars for time complexity estimates. We did not think that parameter uncertainties were relevant for the scope of this work}
	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
    \answerYes{The caption of Figure \ref{fig:scaling} has the specifications of the laptop used for complexity measurements}
\end{enumerate}

\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
\begin{enumerate}
  \item If your work uses existing assets, did you cite the creators?
    \answerYes{\texttt{BifurcationKit.jl} \cite{Veltz2020BifurcationKit.jl} for continuation, \texttt{ForwardDiff.jl} \cite{Revels2016Forward-ModeJulia} for automatic differentiation and \texttt{Flux.jl} \cite{Innes2018FashionableFlux,Innes2018Flux:Julia} for optimisation}
  \item Did you mention the license of the assets?
    \answerNo{MIT Licences}
  \item Did you include any new assets either in the supplemental material or as a URL?
    \answerYes{Julia package implementing our method \href{https://github.com/gszep/BifurcationFit.jl}{\texttt{github.com/gszep/BifurcationFit.jl}}}
  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
    \answerNA{No data was collected}
  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
    \answerNA{No data was collected}
\end{enumerate}

>>>>

\item If you ran experiments...
\begin{enumerate}
  \item Did you include the code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL)?
    \answerYes{Figures can be reproduced using unit tests in the GitHub repository for \texttt{BifurcationInference.jl}}
  \item Did you specify all the training details (e.g., data splits, hyperparameters, how they were chosen)?
    \answerYes{In Section \ref{section:results} we details of optimisations with \texttt{Flux.jl}}
	\item Did you report error bars (e.g., with respect to the random seed after running experiments multiple times)?
    \answerYes{In Section \ref{section:results} we include error bars for time complexity estimates. We did not think that parameter uncertainties were relevant for the scope of this work}
	\item Did you include the total amount of compute and the type of resources used (e.g., type of GPUs, internal cluster, or cloud provider)?
    \answerYes{The caption of Figure \ref{fig:scaling} has the specifications of the laptop used for complexity measurements}
\end{enumerate}

\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
\begin{enumerate}
  \item If your work uses existing assets, did you cite the creators?
    \answerYes{\texttt{BifurcationKit.jl} \cite{Veltz2020BifurcationKit.jl} for continuation, \texttt{ForwardDiff.jl} \cite{Revels2016Forward-ModeJulia} for automatic differentiation and \texttt{Flux.jl} \cite{Innes2018FashionableFlux,Innes2018Flux:Julia} for optimisation}
  \item Did you mention the license of the assets?
    \answerNo{MIT Licences}
  \item Did you include any new assets either in the supplemental material or as a URL?
    \answerYes{Julia package implementing our method \href{https://github.com/anon/Code.jl}{\texttt{Julia package in attached zip file}}}
  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
    \answerNA{No data was collected}
  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
    \answerNA{No data was collected}
\end{enumerate}
